A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-07 pilot-publication/manuscript.Rmd
Start drafting pilot publication results

The protocol was published in BMJ Open [@GerdinWärnberg2022] and was
registered with Clinical Trials Registry - India (reg. no XXX) and
ClinicalTrials.gov (reg. no XXX). Amendments to the protocol after
publication were determined by the core research group and updated on
Clinical Trials Registry - India and ClinicalTrials.gov. Substantial
amendments, such as modifications to the eligibility criteria or
outcomes will also be resubmitted to the journal. Declaration of
interest will be submitted from all participating researchers both in
the core team and at each site.

@@

# Results

>>>>

The protocol was published in BMJ Open [@GerdinWärnberg2022] and was
registered with ClinicalTrials.gov (reg. no NCT05417243). Amendments
to the protocol after publication were determined by the core research
group and updated on ClinicalTrials.gov.

@@

# Results
Between X and X, we enrolled X trauma patients from X participating
centres. The ATLS arm enrolled X patients, the PTC arm X patients, and
the standard care arm X patients. The study flowchart is shown in
Figure X and sample characteristics across trial arms are shown in
Table X. Overall, the number of females were X (X%), the median age
was X (IQR X), and the median ISS was X (IQR X). A total of X (X%)
patients had the primary outcome of mortality at 30 days after arrival
to the emergency department.

## Patient Participant Outcomes
In the post training period, a total of X (X%) patients in the ATLS
arm had the primary outcome, compared to X (X%) patients in the PTC
arm, and X (X%) patients in the standard care arm. The differences
between the arms were X (95% CI X - X) between the ATLS and PTC arms,
X (95% CI X - X) between the ATLS and standard care arms, and X (95%
CI X - X) between the PTC and standard care arms. The change from
baseline for the primary outcome was X in the ATLS arm, X in the PTC
arm, and X in the standard care arm. The differences between changes
from baseline were X (95% CI X - X) between the ATLS and PTC arms, X
(95% CI X - X) between the ATLS and standard care arms, and X (95% CI
X - X) between the PTC and standard care arms. Table X shows
differences in the primary outcome between trial arms with 75, 85, and
95% CIs. Differences in secondary outcomes between trial arms and
subgroups are available as Supplementary material X.

## Resident Participant Outcomes
A total of X residents were trained during this pilot. Overall their
confidence in managing trauma patients was X (IQR X - X) on

## Feasibility Outcomes
